Damage localization based on vibrations

### 2017-04-18 rapport/paper.tex
MAJ paper

Figure \ref{frf_freq} presents results of the FRF on the simulation data: here is the curve of the FRF of one sensor, against frequencies. We can see peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.

Remake figure.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/persensor1.png}
  \caption{FRF of one sensor (ten in total), against frequencies}
  \label{frf_freq}
\end{figure}

@@

Figure \ref{pred} shows the predictive positive factor. We can see that the R method is the best.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/pred.png}
  \caption{Predictive factor}
  \label{pred}
\end{figure}

Figure \ref{pred_neg} shows the predictive negative factor with this method. We can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/pred_neg.png}
  \caption{Predictive negative factor}
  \label{pred_neg}
\end{figure}

@@

Figure \ref{pred_max} shows the predictive factor with this method. We can see that all the method reach 1 at 30\% of damage. That is what you wanted to obtain with this method.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/pred_max.png}
  \caption{Predictive factor}
  \label{pred_max}
\end{figure}

Figure \ref{pred_neg_max} shows the predictive negative factor with this method. We can see that this factor is similar at the factor for the initial methods. It could be worst, but it's not the case.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/pred_neg_max.png}
  \caption{Predictive negative factor}
  \label{pred_neg_max}
\end{figure}

We have here improved the methods, because we eliminate the false positives. The only requirement is to have a detection method.

@@

In this paper, we presented the structure heatlh monitoring and a state of the art for this. Then we detailed one of the methods, the FRF interpolation method, and some physical models. Last, we presented our simulation with a sping-mass system and our results with the implementation of the FRF interpolation method.

%\appendices
%\section{One appendix}
%some text for the appendix.

% use section* for acknowledgement
%\section*{Acknowledgment}
%The authors would like to thank...

%\begin{thebibliography}{1}
%
%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%
%\end{thebibliography}

\nocite{*}
\printbibliography

>>>>

Figure \ref{frf_freq} presents results of the FRF on the simulation data: here is the curve of the FRF of one sensor, against frequencies. We can see peaks which are at the natural frequencies of the system.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/frf_one_sensor.png}
  \caption{FRF of one sensor against frequencies}
  \label{frf_freq}
\end{figure}

Figure \ref{frf_sensors} presents results of the FRF for all the sensors at one frenquency. Curves aren't as regular as the theoretical FRF, but we can see clearly the iregularity between sensors 6 and 7 (there is 10\% of damage here).

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/frf_one_frequency.png}
  \caption{FRF for one frequency against sensors}
  \label{frf_sensors}
\end{figure}

@@

Figure \ref{pred} shows the predictive positive and negative factors. For the positive one, we can see that the R method is the best. For the negative one, we can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/pred.png}
  \includegraphics[width=0.4\textwidth]{images/pred_neg.png}
  \caption{Predictive positive and negative factors}
  \label{pred}
\end{figure}

%Figure \ref{pred_neg} shows the predictive negative factor with this method. 
%\begin{figure}[h!]
%  \centering
%  \caption{Predictive negative factor}
%  \label{pred_neg}
%\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/pred_max.png}
  \includegraphics[width=0.4\textwidth]{images/pred_neg_max.png}
  \caption{Predictive positive and negative factors with elimination of false positives}
  \label{pred_max}
\end{figure}

Figure \ref{pred_max} shows the predictive factors with this method. For the positive one, we can see that all the method reach 1 at 30\% of damage. That is what you wanted to obtain with the elimination of the false positives. For the negative one, we can see that this factor is similar at the factor for the initial methods.

We have here improved the methods, because we eliminate the false positives. The only requirement is to have a detection method. We can notice that all the methods are perfect with damage extent higher than 30\%: in this case, the methods always have a correct localization.

@@

In this paper, we presented the structure health monitoring and a state of the art for this. Then we detailed one of the methods, the FRF interpolation method, and some physical models. Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analized them.

%nombre de capteurs, fréquences à considérer
We have seen that the FRF interpolation method works, and we proposed a method for eliminate the false positives, and improve its performance. But we have seen that under 10\% of damage, this method doesn't detect damages all the time. To improve the method on that, a study of the considered frequencies could be usefull. Indeed, we have considered all the frequencies under the maximal frequency of the structure here. A selection of the frequencies could permit to detect damages under 10\% extent.

Another way to study is the impact of the number of sensors on the efficiency of the method. Here, we were placed in the ideal case where there is a sensor on each mass. For practice cases, the efficiency of the method with less sensors (for example, one sensor for two masses) should be studied.

%\nocite{*}
\printbibliography
